Niche complementarity between pollinators increases plant reproductive success

### 2019-07-30 paper_round2.Rmd
Make two small comments about using incidence vs visits.

d.vis<-ddply(d, c("Site_ID", "Plant_gen_sp"), summarise,
            tot.visits= sum(Frequency))

@@

  web <- table(temp2$Pollinator_gen_sp, temp2$Plant_gen_sp)

  ni<-niche.overlap(web, method="morisita") #THIS SHOULD BE EXPLAINED IN METHODS
  df <- melt(as.matrix(ni), varnames = c("row", "col"))
  df$row<-as.character(df$row)
  df$col<-as.character(df$col)

>>>>

d.vis<-ddply(d, c("Site_ID", "Plant_gen_sp"), summarise,
            tot.visits= sum(Frequency))
#Here you use visits. Which I agree.

@@

  web <- table(temp2$Pollinator_gen_sp, temp2$Plant_gen_sp)
  #SAME HERE, We are assuming INCIDENCE. No Visitation rates.
  #colSums(web)
  #rowSums(web)
  ni<-niche.overlap(web, method="morisita") #THIS SHOULD BE EXPLAINED IN METHODS
  df <- melt(as.matrix(ni), varnames = c("row", "col"))
  df$row<-as.character(df$row)
  df$col<-as.character(df$col)
